\documentclass[a4paper, oneside, final]{scrartcl}

\KOMAoptions{fontsize=10pt}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,    
    urlcolor=blue
}

\usepackage[top=1.55cm, bottom=0.9cm, left=2cm, right=2cm]{geometry}
\usepackage{soul}
\usepackage{titlesec}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\usepackage{scrpage2}
\usepackage{tabularx}

\pagestyle{scrheadings}

\newcommand{\nasc}[2]{\href{#1}{\color{blue}\setulcolor{blue}\ul{#2}}}
\newcommand{\rawnasc}[1]{\nasc{#1}{#1}}
\newcommand{\bearna}[0]{\vspace{2.25mm}\\}
\newcommand{\fmtdate}[1]{\textit{#1}}
\newcommand{\fmtaddress}[1]{\textit{#1}}
\newcommand{\fmtjobtitle}[1]{\textbf{#1}}
\newcommand{\fmtblurb}[1]{\textit{#1}}
\newcommand{\fmtskill}[1]{\textbf{#1}}
\newcommand{\fmtcompetition}[1]{\textbf{\small{#1}}}
%\newcommand{\fmtcompetition}[1]{#1}

\begin{document}

% gets rid of indentation of first line
\raggedright

% Header section. Name on left, contact details on right
\begin{tabularx}{\columnwidth}{@{}XX@{}}
\textsc{\Huge{Noah Ó Donnaile}}&
{\begin{tabularx}{\linewidth}{@{}@{}>{\raggedleft}X@{}} \rawnasc{https://noah.needs.money}\\
\rawnasc{https://github.com/iandioch}\\
\textit{\nasc{mailto:iandioch11+cv@gmail.com}{iandioch11@gmail.com}}
\end{tabularx}}
\end{tabularx}
\vspace{-2em}

\if false
\section{Overview}
I am a capable and amicable full-stack developer with an interest in NLP. My successes in algorithmic programming contests show my enthusiasm and ability in tackling difficult new problems.\\
\fi

% part 4 = https://web.archive.org/web/20120101153859/http://stefano.italians.nl:80/archives/date/2008/10
\section{Experience}
\fmtjobtitle{SWE Intern - Google Assistant Natural Language Generation\hfill Google Switzerland}\\
\fmtdate{June 2019 -- August 2019}\hfill\fmtaddress{Zürich, Switzerland}\\
Ongoing. \fmtskill{C++}, \fmtskill{Typescript}.
\bearna
\fmtjobtitle{Intern in Tools \& Resources for Irish Language Technology\hfill ADAPT Research Centre}\\
\fmtdate{June 2018 -- July 2018}\hfill\fmtaddress{Dublin, Ireland}\\
Cleaned text with \fmtskill{Python}, aligned with \fmtskill{Hunalign}. Extracted Irish multi-word expressions from corpora. \nasc{http://mycode.doesnot.run/2018/08/15/yes-no/}{Created tool to process yes/no questions in Irish} (which lacks words for "yes" \& "no") for a SMT system.
\bearna
\fmtjobtitle{SWE Intern - Google Trips\hfill Google Switzerland}\\
\fmtdate{June 2017 -- May 2018}\hfill\fmtaddress{Zürich, Switzerland}\\
Added Spotlight Search integration, ``view search history" feature, and granular notifications to the Google Trips iOS app in \fmtskill{Objective C} with \fmtskill{Mercurial}.
\bearna
\fmtjobtitle{STEP Intern - Video Ads Engineering Productivity\hfill Google Switzerland}\\
\fmtdate{July 2016 -- September 2016}\hfill\fmtaddress{Zürich, Switzerland}\\
Developed a tool to reduce dependency bloat by splitting large disjoint libraries into small ones. Worked in \fmtskill{Java} (+ \fmtskill{Guice}), \fmtskill{Python} (+ \fmtskill{Flask}), \fmtskill{Javascript}, with \fmtskill{Piper}.
\bearna
\fmtjobtitle{Java Developer\hfill Opening.io}\\
\fmtdate{July 2015 -- August 2015}\hfill\fmtaddress{Dublin, Ireland}\\
Developed \fmtskill{Java} tools to predict a person's salary from their résumé (with \nasc{https://github.com/haifengl/smile}{SMILE} linear regression), and to extract their education information from it (with \fmtskill{Elasticsearch}). Used \fmtskill{Gearman}, \fmtskill{Couchbase}, \fmtskill{git}.
\if false
\bearna
\newcolumntype{D}{>{\raggedleft\arraybackslash}p{.265\linewidth}}
%TODO: reorder rows, perhaps do TITLE DATE COMPANY column order too
\begin{tabularx}{\columnwidth}{@{}p{.2\linewidth}XD@{}}
\fmtjobtitle{Teaching Assistant}&CA117: Computer Programming II (\fmtskill{Python}), DCU&\fmtdate{January 2017 -- May 2017}\\
\fmtjobtitle{Chairperson}&Redbrick Computing \& Networking Society, DCU&\fmtdate{April 2016 -- April 2017}\\
\fmtjobtitle{Teaching Assistant}&CA116: Computer Programming I (\fmtskill{Python}), DCU&\fmtdate{October 2016 -- December 2016}\\
\fmtjobtitle{Secretary}&Redbrick Computing \& Networking Society, DCU &\fmtdate{April 2015 -- April 2016}\\
\fmtjobtitle{Teaching Assistant}&ComputeTY (\fmtskill{Java}), DCU&\fmtdate{January 2016}\\
\fmtjobtitle{Private Tutor}&CA117 (\fmtskill{Python}), \nasc{https://www.100minds.org/campaigns/2016/participants/noah-donnelly}{with proceeds for charity}&\fmtdate{January 2016 -- May 2016}
\end{tabularx}
\fi

\section{Education}
\fmtjobtitle{BSc. in Computational Problem Solving \& Software Development\hfill Dublin City University}\\
\fmtdate{September 2015 -- June 2019}\hfill\fmtaddress{Dublin, Ireland}\\
CPSSD is the only degree in Ireland for undergraduate students with prior CS experience. Read more at \nasc{https://cpssd.net}{the course site I created}. I finished the degree \fmtskill{2\textsuperscript{nd}} in class rankings with an average grade of \fmtskill{89\%}.\\
\fmtskill{Extracurriculars}: 2015-16 \fmtskill{Secretary} and 2016-17 \fmtskill{Chairperson} of computing \& networking society.
\bearna
Earned an \fmtskill{All-Ireland Scholarship} and a \fmtskill{DCU Academic Scholarship} as a result of obtaining 605 points (of 625 maximum; \fmtskill{top 1.2\%} nationally) in the Leaving Certificate in secondary school.

\section{Notable Projects}
\fmtjobtitle{Rabble\hfill Bachelor's Thesis}. 2018 - 2019, 7 months, team of 4\\
\fmtblurb{\nasc{https://github.com/cpssd/rabble}{Rabble} is a decentralised blogging platform focused on breaking echo chambers \& maximising author control}\\
Led development of recommender systems (\fmtskill{Python}, \fmtskill{Jupyter}), and \nasc{http://activitypub.rocks}{Activitypub} interoperability, along with some webserver (\fmtskill{Go}) and database (\fmtskill{SQL}) tasks. Heavily contributed to UI (\fmtskill{Typescript}, \fmtskill{React}).
\bearna
\if false
\fmtjobtitle{Dipla\hfill University Project}. 2016 - 2017, 7 months, team of 4\\
\fmtblurb{\nasc{https://cpssd.net/project/dipla/}{Dipla} is an RPC and distributed computing framework for Python 3.5+}\\
Wrote websocket communications, task queue, transmission of logic to workers (\fmtskill{Python}, \fmtskill{asyncio}, \fmtskill{websockets}), directory server (\fmtskill{Python}, \fmtskill{Flask}), status page (\fmtskill{Javascript}, \fmtskill{ReactJS}, \fmtskill{chart.js}, \fmtskill{jinja2}).
\bearna
%\fi
\fmtjobtitle{safer.place\hfill HackYourWayDay 2017 Hackathon}. Team of 2\\
\fmtblurb{\nasc{http://safer.place}{safer.place} is a website to estimate an Irish address’ safety based on government-provided crime data}\\
Wrote webserver (\fmtskill{Python}, \fmtskill{Flask}, \fmtskill{jinja2}), frontend (\fmtskill{HTML}, \fmtskill{Tachyons CSS}), did data cleanup (\fmtskill{Python}). Translated into Irish. Shortlisted for the \fmtskill{DCU President’s Prize for Innovation 2017}.
\bearna
\fi
\fmtjobtitle{Feedlark\hfill University Project}. 2016, 3 months, team of 5\\
\fmtblurb{\nasc{https://cpssd.net/project/feedlark/}{Feedlark} is a web-based RSS aggregator that promotes items matching topics the user previously liked}\\
Designed and built microservices architecture (\fmtskill{Gearman}), topic modelling (\fmtskill{Python}, \fmtskill{spaCy}), ML recommender system
(\fmtskill{Python}, \fmtskill{Scikit-Learn}), and database service (\fmtskill{Go}, \fmtskill{MongoDB}).
\section{Competitive Programming}
\if false
I am one of the \nasc{https://open.kattis.com/users/iandioch}{top 150 users on Kattis Online Judge}, and am in the 20 highest ranked Irish users (\fmtskill{top 0.66\%} of all users) on Project Euler.
\fi
I \nasc{https://www.computing.dcu.ie/news/irelands-best-young-computer-programmers-win-trip-compete-olympics-programming}{represented Ireland} at the \fmtskill{2015 International Olympiad in Informatics} in Almaty, Kazakhstan. I have also had the following results in other competitions:
\bearna
\newcolumntype{T}{>{\raggedleft\arraybackslash}p{.25\linewidth}}
\newcolumntype{P}{>{\raggedleft\arraybackslash}p{.0875\linewidth}}
\small{}
\begin{tabularx}{\columnwidth}{@{}X|X@{}}
\fmtcompetition{Student Battle Dev Season 13}\hfill 89\textsuperscript{th} place&
\fmtcompetition{ACM IrlCPC 2018}\hfill 1\textsuperscript{st} place\\
\fmtcompetition{HashCode 2019 Qual.}\hfill 211\textsuperscript{th} place, 1\textsuperscript{st} Irish team&
\fmtcompetition{ICPC NWERC 2018}\hfill 55\textsuperscript{th} place, 1\textsuperscript{st} Irish team\\
\fmtcompetition{Student Battle Dev Season 12}\hfill 57\textsuperscript{th} place&
\fmtcompetition{ICPC UKIEPC 2018}\hfill 13\textsuperscript{th} place, 1\textsuperscript{st} Irish team\\
\fmtcompetition{Student Battle Dev Season 11}\hfill\nasc{http://mycode.doesnot.run/2018/03/28/student-battle-dev-season-11/}{41\textsuperscript{st} place}&
\fmtcompetition{ACM IrlCPC 2018}\hfill\nasc{http://mycode.doesnot.run/2018/03/11/irlcpc-2018/}{1\textsuperscript{st} place}\\
\fmtcompetition{ICPC NWERC 2017}\hfill\nasc{http://www.computing.dcu.ie/news/dcu-computing-teams-compete-european-stage}{47\textsuperscript{th} place. 1\textsuperscript{st} Irish team}&
\fmtcompetition{ICPC UKIEPC 2017}\hfill\nasc{https://www.computing.dcu.ie/news/dcu-clinch-top-3-spots-irish-end-ukiepc-2017}{3\textsuperscript{rd} Irish team}\\
\fmtcompetition{ACM IrlCPC 2017}\hfill\nasc{http://mycode.doesnot.run/2017/04/03/irlcpc-2017/}{3\textsuperscript{rd} place}&
\fmtcompetition{HashCode 2017 Qual.}\hfill\nasc{http://mycode.doesnot.run/2018/01/04/hashcode-2017/}{164\textsuperscript{th} place. 1\textsuperscript{st} Irish team}\\ %&Team of 2\\
\fmtcompetition{ICPC NWERC 2016}\hfill 78\textsuperscript{th} place. 2\textsuperscript{nd} Irish team&
\fmtcompetition{ACM IrlCPC 2016}\hfill 2\textsuperscript{nd} place\\ %&Team of 3\\
\fmtcompetition{HashCode 2016 Qual.}\hfill 120\textsuperscript{th} place. 2\textsuperscript{nd} Irish team&
\fmtcompetition{ICPC NWERC 2015}\hfill 74\textsuperscript{th} place. 1\textsuperscript{st} Irish team\\ %&Team of 3\\
\fmtcompetition{Google Call to Code 2014}\hfill 6\textsuperscript{th} place\\%&Solo
\end{tabularx}
\normalsize{}

\end{document}
